Deriving Multi-Headed Projective Dependency Parses \\ from Link Grammar Parses

### 2014-06-03 doc/LinksToDAG.tex
clarified section 1

As recently discussed by \newcite{gomezrodriguez-nivre-2013}, one might impose various requirements on the parse graph:
\begin{itemize}[noitemsep]
\item {\sc Single-Head}: each word has $\leq 1$ parent
\item {\sc Acyclic}: there are no directed cycles
\item {\sc Connected}: each pair of words has a undirected path between them
\item {\sc Reachable}: each word can be reached from 0 by a directed path
  \noteJE{note that this implies connected?  or does connected not allow 0 words on the path, i.e., does it restrict 0 to one child, and if not, is there a principle for that?  If no one, mention in footnote 1.}
\item {\sc Planar}: edges may not ``cross'' \\ (if there are edges between $i,j$ and between $u,v$, where $i < u < j$, then $i \leq v \leq j$)
\end{itemize}
It is common to impose all of these requirements at once, leading to a {\em projective dependency parser} that produces projective trees rooted at 0.\footnote{{\sc Projective} basically means {\sc Planar} + {\sc Reachable}.}  However, parsing algorithms can be devised that relax any or all of the requirements \cite{gomezrodriguez-nivre-2013}.

@@

>>>>

As recently discussed by \newcite{gomezrodriguez-nivre-2013}, one might impose various requirements on the parse graph:
\begin{itemize}[noitemsep]
\item {\sc Single-Head}: each word has $\leq 1$ parent
\item {\sc Acyclic}: there are no directed cycles
\item {\sc Connected}: each pair of words has a undirected path between them
\item {\sc Reachable}: each word can be reached from 0 by a directed path ($\Rightarrow$ {\sc Connected})
\item {\sc Planar}: edges may not ``cross''\footnote{That is, if there are edges between $i,j$ and between $u,v$, where $i < u < j$, then {\sc Planar} requires $i \leq v \leq j$.}
\end{itemize}
It is common to impose all of these requirements at once, leading to a {\em projective dependency parser} that produces projective trees rooted at 0.\footnote{{\sc Projective} basically means {\sc Planar} + {\sc Reachable}.  Note: It does not prevent 0 from having multiple children.}  However, parsing algorithms can be devised that relax any or all of the requirements \cite{gomezrodriguez-nivre-2013}.

@@

\NoteJE{improve table formatting}
